### 2019-09-22 conflog.tex
adds transportation info

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
  \item \textbf{Engineering Hall}\\
  \item \textbf{The I-Hotel}\\
  \item \textbf{}\\
\end{itemize}
\subsection{Conference Contingency Plan}
\subsection{Hotels and Accomodations}
\subsection{Travel and Transportation}

>>>>

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
  \item \textbf{Beckman Institute}\\
  \item \textbf{The I-Hotel}\\
  \item \textbf{}\\
\end{itemize}

\subsection{Conference Contingency Plan}
\subsection{Hotels and Accomodations}

$\Large\textbf{Illini Union}$\\

$\Large\textbf{Marriott TowneSuites}$\\

$\Large\textbf{Hyatt}$\\

\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Below are the round-trip, non-stop, airfare costs for the first weekend of April.  
\begin{center}
	\begin{tabular}{lcc}
		\hline\hline
		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
		\hline\hline
		University of Florida & Orlando (ORL) & $\$$ 236\\
		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
		Penn State University & State College (SCE) & $\$$ 349\\
		MIT & Boston (BOS) & $\$$ 217\\
		UNLV & Las Vegas (LAS) & $\$$ 308\\
		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
		University of Michigan & Detroit (DTW) & $\$$ 240\\
		Oregon State University & Portland (PDX) & $\$$ 355\\
		RPI & Albany (ALB) & $\$$ 504\\
		UC Berkley & Oakland (OAK) & $\$$ 674\\
		UC Irvine & Orange County (SNA) & $\$$ 439\\
		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
		University of Nevada & Reno (RNO) & $\$$ 374\\
		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
		NC State  University & Raleigh (RDU) & $\$$ 195\\
		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
		Clemson University & Greenville (GSP) & $\$$ 295\\
		SC State University & Columbia (CAE) & $\$$ 365\\
		University of South Carolina & Columbia (CAE) & $\$$ 365\\
		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
	\end{tabular}	
\end{center}
\textbf{*}\textit{These fares are predicted to go down around February and March.}\\

Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities. 
\begin{center}
	\begin{tabular}{l r}
	\hline\hline
	\textbf{School}& \textbf{Drive Time}\\
	\hline\hline
	U. Tennessee Knoxville & 7 h 13 min\\
	University of Michigan & 5 h 24 min\\
	Clemson University & 10 h 5 min\\
	U. Missouri-Columbia & 4 h 18 min\\
	Georgia Tech University & 8 h 54 min \\
	University of Pittsburgh & 7 h 19 min\\
	U. Wisconsin-Madison & 3 h 53 min \\
	Penn State University & 9 h 17 min\\
	University of South Carolina& 10 h 44 min\\
	Iowa State University & 5 h 24 min \\
	University of Iowa & 3 h 34 min\\
	Vanderbilt University & 5 h 18 min\\
	\end{tabular}
\end{center}

### 2019-09-22 management.tex
adds transportation info

Committee members should hold professionalism at the forefront of their composure in order to avoid and resolve issues amicably without the involvement of higher powers. As such, members are encouraged to settle conflicts without invoking this protocol. If an issue arises that immediately presents itself as overwhelming, the scope of the issue exceeds an individual’s ability to handle it, or the issue imposes certain implications that jeopardizes the mission of the planning committee, members should not hesitate to refer to this section. In the event of a conflict between members of the planning committee, a document for decision-making and
conflict resolution has been drafted and approved by the general committee. All General Committee members
are expected to abide by the resolution. Key points of the resolution are as follows:
\begin{enumerate}
	\item Subcommittees are encouraged to operate as autonomous and democratic as possible; however, the General
	Co-Chairs reserve the rights to make all final decisions. If the Co-Chairs cannot agree, the faculty advisor will be involved.
	\item Conflicts between committee members are to be resolved outside of the committee. Should this begin to
	affect the work of these members, the General Co-Chairs may intervene.
	\item Any cases of misconduct or negligence will be handled by the General Co-Chairs as necessary.
	\item For extreme cases of misconduct or negligence, separate steps for the removal and replacement of a
	member are outlined for general members, Subcommittee Chairs, and General Co-Chairs. These include
	a discussion with the offending member, consultation of the Faculty Advisor, and a hearing with the
	General Committee to decide if removal is necessary.
\end{enumerate}

>>>>

Committee members should hold professionalism at the forefront of their composure in order to avoid and resolve issues amicably without the involvement of higher powers. As such, members are encouraged to settle conflicts without invoking this protocol. If an issue arises that immediately presents itself as overwhelming, the scope of the issue exceeds an individual’s ability to handle it, or the issue imposes certain implications that jeopardizes the mission of the planning committee, members should not hesitate to refer to this section. In the event of a conflict between members of the planning committee, a document for decision-making and
conflict resolution has been drafted and approved by the general committee. All General Committee members
are expected to abide by the resolution. Key points of the resolution are as follows:
\begin{enumerate}
	\item Subcommittees are encouraged to resolve conflicts internally and as democratically as possible. If an independent resolution cannot be reached, the Co-Chairs should be involved. The Co-Chairs have the final word on all decisions. If the Co-Chairs are unable to agree on a solution, the faculty advisor will be involved.
	\item Conflicts between individual committee members are to be resolved outside of the committee. Should such a conflict jeopradize the mission of the conference the Co-Chairs will be involved. 
	\item Any cases of misconduct or negligence will be handled appropriately by the Co-Chairs.
	\item For extreme cases of misconduct or negligence, separate steps for the removal and replacement of a
	member are outlined for general members, Subcommittee Chairs, and Co-Chairs. These include
	a discussion with the offending member, consultation of the Faculty Advisor, and a hearing with the
	General Committee to decide if removal is necessary.
\end{enumerate}
